---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# eepd

<!-- badges: start -->
<!-- badges: end -->

```{r setup}
library(eepd)
data("ptpdata")
```

## Supplying models

We can specify the models to test using `eepd_mod()`. This create a full cross of all supplied arguments, which include model formula, families, whether the outcome is logged or not, whether fixed effects are included or not, whether the outcome should be a difference, and whether outcome lags shoudl appear as predictors. Below, we create a cross of 9 models.

```{r}
models <- eepd_mod(list(deaths ~ 1,
                        deaths ~ 1 + year,
                        deaths ~ 1 + poly(year, 2)),
                   family = list("gaussian", "quasipoisson"),
                   log = c(TRUE, FALSE),
                   lag = 0, diff_k = 0, fixef = TRUE)

models
```

Normally, this cross would yield 12 = 3 (formulas) x 2 (families) x 2 (log T/F), but by default any models with non-linear links and `log = TRUE` are removed, leaving 9 models. If we want to manually add other models, we can so by creating a new models object and appending it to the current one.

```{r}
models2 <- eepd_mod(list(deaths ~ 1),
                    diff_k = 1)

models <- c(models, models2)

models
```

This leaves us with 10 models.

## Fitting the models

Next we fit all 10 models to the data. We do so once for each validation time to compute the average prediction error that will be used to select the optimal model later. We also do so for the final evlauation time to compute the ATT. All models are fit simultaneously so the simulation can use the full joint distribution of model parameter estimates. For each validation time, each model is fit using a dataset that contains data points prior to that time. In a later step, the average absolute prediction error will be computed at the corresponding validation time.

We use `eepd_fit()` to fit the models.

```{r}
fits <- eepd_fit(models, data = ptpdata,
                 group_var = "group",
                 time_var = "year",
                 val_times = 2004:2007,
                 post_time = 2008,
                 unit_var = "state")
```

NOTE: add a print method

## Selecting the optimal model and computing the ATT

We select the optimal model by computing the average absolute predictions errors for each model and validation time and choose choose the optimal model as that which has lowest maximum average absolute preidciton error across validation times. Then, we compute the ATT from this model.

`eepd_sim()` does this when the `nsim` argument is set to 0 (which it is by default). In this case, no simulation is done and the model selection is treated as fixed. We do not get a distribution of ATTs, just a single ATT chosen as that computed from the optimal model.

```{r}
est <- eepd_sim(fits)

plot(est)

est
```

## Simulating Model Selection

Given that the resulting ATT does not account for variability in model selection, we can also simulate model selection by drawing coefficients from the joint posterior of all fitted models and performing model selection and calculating the ATT in each simulation. We can do this simply by supplying an argument to `nsim` indicating the number of simulations. More is better but takes longer. We can supply an argument to `cl` to engage parallelization and set `verbose = TRUE` to request a progress bar.

```{r}
est_sim <- eepd_sim(fits, nsim = 300, cl = 4)

est_sim

plot(est_sim, palette = "Paired")
```

Printing the output produces the estimate of the ATT computed using the optimal model in each simulation averaged across all simulations. The plot displays a density of the estimates colored by model and the distribution of which models were most frequently determined to be optimal.

## Bootstrapping the whole thing

We can bootstrap the whole thing using `eepd_boot()`. By default, this uses the fractional weighted bootstrap as implement in `fwb::fwb()` to draw bootstrap samples and perform model fitting, simulation, model selection, and computation of the ATT, yielding a distribution of ATTs from which one can perform inference.

`eepd_boot()` takes in the same arguments as `eepd_fit()` as well as `nboot` for the number of bootstrap replications and `nsim` for the number of simulation to do within each each bootstrap sample.

```{r}
boot_fits <- eepd_boot(models, data = ptpdata,
                       nboot = 199, nsim = 50,
                       group_var = "group",
                       time_var = "year",
                       val_times = 2004:2007,
                       post_time = 2008,
                       unit_var = "state",
                       cl = 4, verbose = T)

summary(boot_fits, ci.type = "perc")
```

The output is a `fwb_boot` object that can be examined using tools from `fwb`, such as `summary()`, which produces the point estimate (computed on the original dataset) and confidence interval.